\thispagestyle{empty}
\vspace*{\fill}
\small

\textbf{Acknowledgments:} \\

The research presented in this thesis was performed within the Rotterdam Study. We gratefully acknowledge the contributions of the study participants, staff, participating general practitioners, and pharmacists involved in all studies.

Publication of this thesis was kindly supported by the Department of Epidemiology of the Erasmus Medical Center and by the Erasmus University Rotterdam. \\


\textbf{ISBN:} 978-94-6419-511-8\\
\textbf{Printing:} Gildeprint BV, Enschede\\  
\textbf{Cover art:} Inspired by Judea Pearl's 
"The Ladder of Causation". Illustrated by Lucia Mayorga Garrido Cortés \\

\textbf{\copyright Liliana Paloma Rojas Saunero, 2022.} \\

For all articles published, the copyright has been transferred to the respective publisher. No part of this thesis may be reproduced, stored in a retrieval system, or transmitted in any form or by any means, without written permission from the author or, when appropriate, from the publisher. \\

This thesis was typeset using Markdown, \LaTeX\ and the \verb+bookdown+ R-package

\newpage
\thispagestyle{empty}
\begin{center}
\vspace{20mm}

\title{\textbf{\Large Dementia Research Under \\ \vspace{5mm} A Causal Inference Lens}}

\textit{\large Onderzoek naar dementie onder een causale inferentielens}

\vspace{10mm}
\textbf{\large{Proefschrift}}\\
\vspace{10mm}
ter verkrijging van de graad van doctor aan de\\
Erasmus Universiteit Rotterdam\\
op gezag van de\\
rector magnificus\\
\vspace{10mm}
Prof.dr. A.L. Bredenoord\\
\vspace{10mm}
en volgens besluit van het College voor Promoties.\\
De openbare verdediging zal plaatsvinden op\\
\vspace{10mm}
woensdag 8 juni 2022 om 15.30 uur\\
\vspace{10mm}
door\\
\vspace{10mm}
Liliana Paloma Rojas Saunero\\
geboren te La Paz, Bolivia. 
\end{center}

\ThisLLCornerWallPaper{0.45}{figs/eur_line.pdf}
\ThisLRCornerWallPaper{0.4}{figs/eur_logo.pdf}

 

\newpage
\begin{flushleft}
\textbf{\large{Promotiecommissie}}\\
\vspace{10mm}
  \textbf{Promotoren:} \hspace{6mm} Prof.dr. M.A. Ikram \\
\vspace{10mm}
\textbf{Overige leden:} \hspace{3.5mm} Prof.dr. M.K. Ikram \\
\hspace{29mm} Dr. E.R. Mayeda \\
\hspace{29mm} Dr. J.G. Young\\
\vspace{10mm}
\textbf{Copromotor:} \hspace{6mm} Dr. S.A. Swanson\\
\end{flushleft}
\vspace*{\fill}



\vspace*{\fill}
 
\textbf{Paranimfen:} \hspace{2.5mm}Irma Karabegovic   \\ 
\phantom{Paranimfen} \hspace{6.5mm}Banafsheh Arshi    
                    
\newpage  
\thispagestyle{empty}
\textbf{Manuscripts that form the basis of this thesis}

Caniglia E.C., \textbf{Rojas-Saunero L.P.}, Hilal S., Licher S., Logan
R., Stricker B., Ikram M.A., Swanson S.A.
\href{https://pubmed.ncbi.nlm.nih.gov/32753444/}{Emulating a target
trial of statin use and risk of dementia using cohort data}.
\emph{Neurology.} 2020;95(10):e1322-e1332. (Chapter 2)

\textbf{Rojas-Saunero L.P.}, Hilal S., Murray E.J., Logan R.W., Ikram
M.A., Swanson S.A.
\href{https://pubmed.ncbi.nlm.nih.gov/33247419/}{Hypothetical
blood-pressure-lowering interventions and risk of stroke and dementia}.
\emph{European Journal of Epidemiology.} 2021;36(1):69-79. (Chapter 3)

\textbf{Rojas-Saunero L.P.}, van der Willik K.D., Schagen S.B., Ikram
M.A., Swanson S.A. Towards a clearer causal question underlying the
association between cancer and dementia. \emph{Submitted} (Chapter 4)

\textbf{Rojas-Saunero L.P.}, Young J.G., Didelez V., Ikram M.A., Swanson
S.A. How are we counting the dead in dementia studies? \emph{Submitted}
(Chapter 5)

\textbf{Rojas-Saunero L.P.}, Young J.G., Didelez V., Ikram M.A., Swanson
S.A. Choosing questions before methods in dementia research with
competing events and causal goals \emph{Submitted} (Chapter 6)

\textbf{Rojas-Saunero L.P.}
\href{https://pubmed.ncbi.nlm.nih.gov/33122553/}{In the midst of two
realities}. \emph{Epidemiology.} 2021;32(1):148-149. (Chapter 8)

\newpage
\thispagestyle{empty}
\tableofcontents
