# Appendix  {#chapter10}

\newpage

## PhD Portafolio {-}

**PhD candidate:** Liliana Paloma Rojas Sauner

**Department:** Department of Epidemiology, Erasmus Medical Center

**PhD period:** February, 2018 - February 2022

**Promotor:** M. Arfan Ikram

**Co-promotor:** Sonja A. Swanson

***

**General courses**

```{r port_t1, echo= FALSE, warning = FALSE, message = FALSE, results='asis'}
library(knitr)
library(kableExtra)
library(magrittr)
library(dplyr)
options(knitr.kable.NA = "")

t_portfolio <- rio::import(here::here("tables", "portfolio.xlsx"))

t_portfolio %>%
  filter(type == "GC") %>% 
  select(-type) %>% 
  rename(`Elective courses` = Activity) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(
    full_width = F,
    position = 'center'
  ) %>%
  column_spec(1, width = "25em") %>% 
  footnote(general = "* 1 ECTS (European Credit Transfer System) equals a workload of 28 hours ") 

```

**International conferences**

```{r port_t2, echo= FALSE, warning = FALSE, message = FALSE, results='asis'}
t_portfolio %>%
  filter(type == "IC") %>% 
  select(-type) %>% 
  rename(Event = Activity) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(
    full_width = F,
    position = 'center'
  ) %>%
  column_spec(1, width = "25em") %>% 
  footnote(general = "* 1 ECTS (European Credit Transfer System) equals a workload of 28 hours ")
```

**Teaching activities**

```{r port_t3, echo= FALSE, warning = FALSE, message = FALSE, results='asis'}

t_portfolio %>%
  filter(type == "TA") %>% 
  select(-type) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(
    full_width = F,
    position = 'center'
  ) %>%
  row_spec(c(0,c(1,5,12)), bold = TRUE) %>% 
  kable_styling(font_size = 9) %>% 
  column_spec(1, width = "25em") %>% 
  footnote(general = "* 1 ECTS (European Credit Transfer System) equals a workload of 28 hours ")

```

**Other activities**

```{r port_t4, echo= FALSE, warning = FALSE, message = FALSE, results='asis'}
t_portfolio %>%
  filter(type =="O") %>% 
  select(-type) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(
    full_width = F,
    position = 'center'
  ) %>%
  row_spec(c(0,c(2,5)), bold = TRUE) %>% 
  kable_styling(font_size = 9) %>% 
  column_spec(1, width = "25em") %>% 
  footnote(general = "* 1 ECTS (European Credit Transfer System) equals a workload of 28 hours ")
```

\clearpage
\newpage

**List of publications**

- **Rojas-Saunero LP**, Hilal S, Murray EJ, Logan RW, Ikram MA, Swanson SA. [Hypothetical blood-pressure-lowering interventions and risk of stroke and dementia](https://pubmed.ncbi.nlm.nih.gov/33247419/). _European Journal of Epidemiology._2020;

- **Rojas-Saunero LP**. [In the midst of two realities](https://pubmed.ncbi.nlm.nih.gov/33122553/).2020;

- Caniglia EC, **Rojas-Saunero LP**, Hilal S, Licher S, Logan R, Stricker B, Ikram MA, Swanson SA. [Emulating a target trial of statin use and risk of dementia using cohort data](https://pubmed.ncbi.nlm.nih.gov/32753444/). _Neurology._ 

- Heshmatollah A, Mutlu U, **Rojas-Saunero LP**, Portegies MLP, Wieberdink RG, Koudstaal PJ, Ikram MK, Ikram MA. [Unspecified Strokes: Time Trends, Determinants, and Long-Term Prognosis in the General Population](https://pubmed.ncbi.nlm.nih.gov/32062655/). _Neuroepidemiology._ 

- Hettne K, Proppert R, Nab L, **Rojas-Saunero LP**, Gawehns G. [ReprohackNL 2019: How libraries can promote research reproducibility through community engagement](https://iassistquarterly.com/index.php/iassist/article/view/977). _IASSIST Quarterly._ 

- Téllez-Rojo MM, Rothenberg SJ , Texcalac-Sangrador JL, Just AC, Kloog I, **Rojas-Saunero LP**, Gutiérrez-Avila I, Bautista-Arredondo LF, Tamayo-Ortiz M, Romero M, Hurtado-Díaz M, Schwartz JD, Wright R, Riojas-Rodríguez H. [Children's acute respiratory symptoms associated with PM2. 5 estimates in two sequential representative surveys from the Mexico City Metropolitan Area](https://pubmed.ncbi.nlm.nih.gov/31711659/). _Environmental Research._ 

- van der Willik KD, **Rojas-Saunero LP.**, Labrecque JA, Ikram MA, Schagen SB, Striker BH, Ruiter R. [Pathology-confirmed versus non pathology-confirmed cancer diagnoses: incidence, participant characteristics, and survival](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7320936/). _European Journal of Epidemiology._ 

- Marciano S, Mauro E, Giunta D, Torres MC, Diaz JM, Bermudez C, Gutierrez-Acevedo MN, Narvaez A, Ortíz J, Dirchwolf M, Pollarsky F, **Rojas-Saunero LP**, Gadano A. [Impact of acute-on-chronic liver failure on post-transplant survival and on kidney outcomes](https://pubmed.ncbi.nlm.nih.gov/31385871/). _European journal of gastroenterology & hepatology._ 2019

- Díaz JM, Boietti BR, Vazquez FJ, Waisman GD, Giunta DH, **Rojas LP**, Peuchot V, Posadas-Martínez ML. [Mean platelet volume as a prognostic factor for venous thromboembolic disease](https://pubmed.ncbi.nlm.nih.gov/31095161/). _Revista Medica de Chile._ 2019

- Mendizabal M, Tagliafichi V, Rubinstein F, **Rojas P**, Marciano S, Yantorno S, Cejas N, Barrabino M, Anders M, Cairo F, Villamil F, Blazquez L, Zerega A, Ferretti S, Fernández D, Paredes S, Aballay Soteras G, Gaite L, Bisigniano L, Silva MO. [Liver transplantation in adults with acute liver failure: Outcomes from the Argentinean Transplant Registry](https://pubmed.ncbi.nlm.nih.gov/31053539/)
_Annals of Hepatology._ 

- [Are there any risk factors for developing complications with the use of retrievable vena cava filters in orthopaedic surgery?](https://pubmed.ncbi.nlm.nih.gov/30273535/)

_Revista de la Facultad de Ciencias Médicas de Córdoba._ Slullitel PAI, Díaz Dilernia F, Stagnaro J, **Rojas LP**, Posadas-Martinez ML, Buttaro MA, Slullitel GA. 2018

- [Medium-term results in the treatment of obesity with an intragastric balloon: cohort study](http://www.actagastro.org/numeros-anteriores/2017/Vol-47-N1/Vol47N1-PDF11.pdf). _Acta Gastroenterológica Latinoamericana._ Gutt S, Argüero MJ, **Rojas LP**, Aragona HS, Tamaroff J, Abecia VH, Marcolongo M. 2017

- [A Dynamic Definition of Acute Kidney Injury Does not Improve Prognosis Assessment in Acutely Decompensated Patients with Cirrhosis](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5478969/). _Journal of clinical and experimental hepatology._ Marciano S, Mauro E, Dirchwolf M, Debernardi ME, Giunta DG, Pagotto V, **Rojas LP**, Gadano A. 2017

- [Distinctions between seeking-and non-seeking-treatment research participants: implications for clinical trials effectiveness](https://pubmed.ncbi.nlm.nih.gov/28662359/). _The American Journal of Drug and Alcohol Abuse._ L Acion, J Zwick, **LP Rojas-Saunero**, S Arndt. 2017

- Gutiérrez Acevedo MN, Peuchot V, Ardiles V, Giunta D, Marciano S, **Rojas Saunero LP**, Waisman GD, Boietti BR, Posadas-Martínez ML. [Incidence of venous thromboembolism in cirrhotic patients ](http://www.actagastro.org/numeros-anteriores/2016/Vol-46-N3/Vol46N3-PDF07.pdf). _Acta Gastroenterológica Latinoamericana._ 2016

- Posadas-Martinez ML, **Rojas LP**, Vazquez FJ, De Quiros FB, Waisman GD, Giunta DH. [Statistical Process Control: A Quality Tool for a Venous Thromboembolic Disease Registry](https://pubmed.ncbi.nlm.nih.gov/27556842/). _Journal of registry management._ 2016

- **Rojas-Saunero LP**, Claros Beltrán N. [Familiar, socioeconomic and gynecologic aspects as risk factors for teenage pregnancy](http://www.scielo.org.bo/scielo.php?script=sci_arttext&pid=S1726-89582014000100004). _Revista Médica La Paz._ 2014

\newpage

## About the author {-}

Liliana Paloma Rojas Saunero was born on 23rd of April, 1989 in La Paz, Bolivia. She was raised around mountains at over 3500 meters above sea level, and obtained her medical degree from the public university "Universidad Mayor de San Andrés". During the last two years of her studies, she was an undergraduate research assistant at Research Institute in Health and Development at the same university. During this time she felt in love with research and epidemiology. For this reason, after obtaining her medical degree in medicine, she moved to Buenos Aires and obtained her master degree in clinical Research. During the same time as her master, she worked as a Research Fellow in the Internal Medicine Research Area, Hospital Italiano de Buenos Aires. She later accepted a position as Associate Researcher Liver Transplant Unit, Hospital El Cruce, at the same time she collaborated as a research assistant for the Center for Nutrition and Health Research, National Institute of Public Health in Mexico. During those two years she  persuit a graduate degree of Specialization in Statistics for Health Sciences. Calculus Institute. University of Buenos Aires
Buenos Aires, Argentina.

During that time she received a the fellowship for the Summer Program at the National Institute of Health Sciences. This visit was trascendental, not because it was the first time 

\newpage

## Acknowledgements {-}