# Appendix  {#chapter10}

\newpage

## PhD Portafolio {-}

**PhD candidate:** Liliana Paloma Rojas Saunero

**Department:** Department of Epidemiology, Erasmus Medical Center

**PhD period:** February, 2018 - February 2022

**Promotor:** M. Arfan Ikram

**Co-promotor:** Sonja A. Swanson

**General Courses**
```{r portt1, echo= FALSE, warning = FALSE, message = FALSE, results='asis'}
library(knitr)
library(kableExtra)
library(magrittr)
library(dplyr)
options(knitr.kable.NA = "")

t_portfolio <- rio::import(here::here("tables", "portfolio.xlsx"))

legend <- "* 1 ECTS (European Credit Transfer System) equals a workload of 28 hours "

t_portfolio %>%
  filter(type == "GC") %>%
  select(-c(3:4)) %>% 
  # select(-type) %>% 
  # rename(`Elective courses` = Activity) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(
    full_width = F,
    position = 'left',
    latex_options = "HOLD_position",
    font_size = 9
  ) %>%
  column_spec(1, width = "8cm") %>%
  row_spec(0,0, bold = TRUE)

```

**International Conferences**
```{r portt2, echo= FALSE, warning = FALSE, message = FALSE, results='asis'}
t_portfolio %>%
  filter(type == "IC") %>% 
  select(-c(3:4)) %>% 
  rename(Event = Activity) %>% 
  mutate(Event = stringr::str_replace(Event, " - Oral presentation", "")) %>% 
  # select(-type) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(
    full_width = F,
    position = 'left',
    latex_options = "HOLD_position",
    font_size = 9
  ) %>%
  row_spec(0,0, bold = TRUE) %>%
  column_spec(1, width = "8cm") %>% 
  footnote(general = "All as oral presentations")
```

\newpage

**Teaching Activities**
```{r portt3, echo= FALSE, warning = FALSE, message = FALSE, results='asis'}

t_portfolio %>%
  filter(type == "TA") %>% 
  select(-c(3:4)) %>% 
  # select(-type) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(
    full_width = F,
    position = 'left',
    latex_options = "HOLD_position",
    font_size = 9
  ) %>%
  row_spec(c(0,c(1,5,12)), bold = TRUE) %>% 
  column_spec(1, width = "8cm")

```

**Other Activities**
```{r portt4, echo= FALSE, warning = FALSE, message = FALSE, results='asis'}
t_portfolio %>%
  filter(type =="O") %>% 
  select(-c(3:4)) %>% 
  # select(-type) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(
    full_width = F,
    position = 'left',
    latex_options = "HOLD_position",
    font_size = 9
  ) %>%
  row_spec(c(0,c(1,3,6)), bold = TRUE) %>% 
  column_spec(1, width = "8cm")
```

\newpage

**List of Publications**

- **Rojas-Saunero LP**, Hilal S, Murray EJ, Logan RW, Ikram MA, Swanson SA. [Hypothetical blood-pressure-lowering interventions and risk of stroke and dementia](https://pubmed.ncbi.nlm.nih.gov/33247419/). _European Journal of Epidemiology._ 2021;36(1):69-79.

- **Rojas-Saunero LP**. [In the midst of two realities](https://pubmed.ncbi.nlm.nih.gov/33122553/). _Epidemiology._ 2021;32(1):148-149.

- Caniglia EC, **Rojas-Saunero LP**, Hilal S, Licher S, Logan R, Stricker B, Ikram MA, Swanson SA. [Emulating a target trial of statin use and risk of dementia using cohort data](https://pubmed.ncbi.nlm.nih.gov/32753444/). _Neurology._ 2020;95(10):e1322-e1332. 

- Heshmatollah A, Mutlu U, **Rojas-Saunero LP**, Portegies MLP, Wieberdink RG, Koudstaal PJ, Ikram MK, Ikram MA. [Unspecified Strokes: Time Trends, Determinants, and Long-Term Prognosis in the General Population](https://pubmed.ncbi.nlm.nih.gov/32062655/). _Neuroepidemiology._ 2020;54(4):334-342.

- Hettne K, Proppert R, Nab L, **Rojas-Saunero LP**, Gawehns G. [ReprohackNL 2019: How libraries can promote research reproducibility through community engagement](https://iassistquarterly.com/index.php/iassist/article/view/977). _IASSIST Quarterly._ 2020;44:1-2.

- Téllez-Rojo MM, Rothenberg SJ , Texcalac-Sangrador JL, Just AC, Kloog I, **Rojas-Saunero LP**, Gutiérrez-Avila I, Bautista-Arredondo LF, Tamayo-Ortiz M, Romero M, Hurtado-Díaz M, Schwartz JD, Wright R, Riojas-Rodríguez H. [Children's acute respiratory symptoms associated with PM2. 5 estimates in two sequential representative surveys from the Mexico City Metropolitan Area](https://pubmed.ncbi.nlm.nih.gov/31711659/). _Environmental Research._ 2020;180:108868.

- van der Willik KD, **Rojas-Saunero LP.**, Labrecque JA, Ikram MA, Schagen SB, Striker BH, Ruiter R. [Pathology-confirmed versus non pathology-confirmed cancer diagnoses: incidence, participant characteristics, and survival](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7320936/). _European Journal of Epidemiology._ 2020;35(6):557–565.

- Marciano S, Mauro E, Giunta D, Torres MC, Diaz JM, Bermudez C, Gutierrez-Acevedo MN, Narvaez A, Ortíz J, Dirchwolf M, Pollarsky F, **Rojas-Saunero LP**, Gadano A. [Impact of acute-on-chronic liver failure on post-transplant survival and on kidney outcomes](https://pubmed.ncbi.nlm.nih.gov/31385871/). _European journal of gastroenterology & hepatology._ 2019;31(9):1157-1164.

- Díaz JM, Boietti BR, Vazquez FJ, Waisman GD, Giunta DH, **Rojas LP**, Peuchot V, Posadas-Martínez ML. [Mean platelet volume as a prognostic factor for venous thromboembolic disease](https://pubmed.ncbi.nlm.nih.gov/31095161/). _Revista Medica de Chile._ 2019;147(2):145-152.

- Mendizabal M, Tagliafichi V, Rubinstein F, **Rojas P**, Marciano S, Yantorno S, Cejas N, Barrabino M, Anders M, Cairo F, Villamil F, Blazquez L, Zerega A, Ferretti S, Fernández D, Paredes S, Aballay Soteras G, Gaite L, Bisigniano L, Silva MO. [Liver transplantation in adults with acute liver failure: Outcomes from the Argentinean Transplant Registry](https://pubmed.ncbi.nlm.nih.gov/31053539/). _Annals of Hepatology._ 2019;18(2):338-344

- Slullitel PAI, Díaz Dilernia F, Stagnaro J, **Rojas LP**, Posadas-Martinez ML, Buttaro MA, Slullitel GA. [Are there any risk factors for developing complications with the use of retrievable vena cava filters in orthopaedic surgery?](https://pubmed.ncbi.nlm.nih.gov/30273535/). _Rev Fac Cien Med Univ Nac Cordoba_. 2018;75(2):119-127.

- Gutt S, Argüero MJ, **Rojas LP**, Aragona HS, Tamaroff J, Abecia VH, Marcolongo M.  [Medium-term results in the treatment of obesity with an intragastric balloon: cohort study](http://www.actagastro.org/numeros-anteriores/2017/Vol-47-N1/Vol47N1-PDF11.pdf). _Acta Gastroenterol Latinoam_. 2017;47(1):58-63

- Marciano S, Mauro E, Dirchwolf M, Debernardi ME, Giunta DG, Pagotto V, **Rojas LP**, Gadano A. [A Dynamic Definition of Acute Kidney Injury Does not Improve Prognosis Assessment in Acutely Decompensated Patients with Cirrhosis](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5478969/). _Journal of clinical and experimental hepatology._ 2017;7(2):135–143.

- Acion L, Zwick J, **Rojas-Saunero LP**, Arndt S. [Distinctions between seeking-and non-seeking-treatment research participants: implications for clinical trials effectiveness](https://pubmed.ncbi.nlm.nih.gov/28662359/). _The American Journal of Drug and Alcohol Abuse._ 2017;43(6):628-630.

- Gutiérrez Acevedo MN, Peuchot V, Ardiles V, Giunta D, Marciano S, **Rojas Saunero LP**, Waisman GD, Boietti BR, Posadas-Martínez ML. [Incidence of venous thromboembolism in cirrhotic patients ](http://www.actagastro.org/numeros-anteriores/2016/Vol-46-N3/Vol46N3-PDF07.pdf). _Acta Gastroenterol Latinoam_. 2016;46:201-204.

- Posadas-Martinez ML, **Rojas LP**, Vazquez FJ, De Quiros FB, Waisman GD, Giunta DH. [Statistical Process Control: A Quality Tool for a Venous Thromboembolic Disease Registry](https://pubmed.ncbi.nlm.nih.gov/27556842/). _Journal of registry management._ 2016;43(2):82-6.

- **Rojas-Saunero LP**, Claros Beltrán N. [Familiar, socioeconomic and gynecologic aspects as risk factors for teenage pregnancy](http://www.scielo.org.bo/scielo.php?script=sci_arttext&pid=S1726-89582014000100004). _Revista Médica La Paz._ 2014; 20(1): 18-27.

\newpage

## Acknowledgments {-}

This book summarizes a fraction of what these four years of doctorate have meant, in terms of learning and growth. When I started this journey, I did not imagine everything that would happen academically, professionally and personally. Now that I look back, this has resulted in the best experience of my life so far. For this reason, I would like to thank deeply those who have being a part of this journey.

To my promotor: Arfan, thank you for believing in my interest and skills and letting me join such an astounding team as a doctoral student. Thank you for always reminding me that the PhD is a unique path for each student, and as such I should embrace, own and enjoy my journey.

To my co-promotor: Sonja, I have no words to thank you for all the support. Thank you for teaching me the fascinating world of causal inference, for supporting me through the learning process and for giving me the security and confidence I needed in moments of frustration and impostor syndrome. Thank you for helping me find my voice, and for showing me that what I saw as weaknesses are actually my strengths. Furthermore, thank you for all the support you have given me when this academic journey converged with personal milestones such as pregnancy and motherhood. Thanks for showing me that it is possible to navigate both worlds and that…wow, it’s worth it.

To my committee: Thank you very much for taking the time to read and review this dissertation. I am honored to have you all as part of the defense and I feel very excited and privileged to learn from your expertise.

To my collaborators: Jessica, Vanessa, Ellie C., Ellie M., Marcia. Thank you for being so generous with your expertise, for your kindness and patience and for taking the time to teach me as much as you all did. You are women that I truly admire.

To my causal inference group: Lizzie, Jeremy, and Kelly. I feel truly lucky for having had the opportunity to share this journey with all of you. Thanks for being such amazing friends and colleagues, for the fun times and for the nerdy (also fun) times. Sharing with you feels like the best reinforcement that epidemiology is the best career one could choose.

To the entire neuroepidemiology group and colleagues on the 28th floor: thank you very much for all the moments shared, thank you for showing me so much about the Dutch culture, you have made my experience in the Netherlands truly unforgettable!

To my dear friends: Irmita termita, my bosnian sister, thanks for being the most unconditional  friend, thanks for feeding me, for teaching me how to squat like a true Balkan, for taking care of me and for always lifting me up when I was feeling low. Lizzie, thanks for being the friend with who I could share all my causal inference fears and grading nightmares, and for being there to watch Ghibli movies and play boardgames. Ani and Nikki, you made of Schiedam our home by being such amazing friends, part of our best memories with Dino are with you guys sharing nature, photography, home cooked meals and our different cultural traditions, and now… baby hacks! Silvi, Marcelo, Banafsheh, Arash, Hamid, Caro and Ale: thank you for being the international family that is always there to help and to celebrate all the milestones of this journey. Lau: thank you for always believing in me and for always being so present, in the good and bad times, giving me security and so much love. 

To my dear friends Adri, Carito, Filo, Yarita, Tere, Martin, Vani, Lu, Cris, Flor, Juli, Luli, Sebas, Diegui, Bruno, no matter the distance you will always have a place in my heart. Thanks for helping me be where I am today. 

To my peers from different communities of practice: MECOR family, MELODEM, R-Ladies, Reprohack, Open Science Community Rotterdam. You made this journey so much more interesting and fun, thanks for your generosity and amiability. 

Ma, Pa y Camilita. Fankiu por siempre animarme a soñar en grande, y por darme alas para vencer las limitaciones geográficas para perseguir mis sueños. Fankiu por todo el apoyo y confianza que me dieron para descubrir mi propio camino y por estar ahí, cuidándome, conteniendome y alentándome, siempre. Su amor incondicional es mi aliento, mi energía y mi motivación. Los amo con todo mi corazón.

Dinito amado, lo que dije alguna vez se intensifica con los años, gracias por enseñarme que la vida es más hermosa cuando el vuelo es compartido. Gracias por saltar conmigo a lo desconocido, por ser mi compañero de aventuras y por siempre creer en mi. Gracias por interesarte por mi trabajo y hasta aprender de los temas de mi tesis. Te amo y no puedo esperar a seguir descubriendo y construyendo esta vida juntos.

Y a mi amada Amarucita, cuando crezcas sabrás que fuiste la fuerza y motivación que mamá necesitaba para escribir esta tesis. Te amo hijita.


\newpage

## About the author {-}

Liliana Paloma Rojas Saunero was born on April 23, 1989 in La Paz, Bolivia. She was raised surrounded by beautiful mountains at over 3400 meters above sea level, and studied medicine at the local public university, Universidad Mayor de San Andrés. During the last two years of her studies, she was an undergraduate research assistant at the Research Institute in Health and Development, where her passion for research began. For this reason, after obtaining her medical degree in 2013, she moved to Buenos Aires, Argentina. There, she obtained her Master Degree in Clinical Research and worked as a Research Fellow in the Internal Medicine Research Area of the Hospital Italiano de Buenos Aires. In 2016, she was appointed as Associate Researcher at Hospital El Cruce, where she lead the efforts to develop an institutional registry for patients with liver diseases and in requirement of transplant. At the same time, she worked remotely as research consultant for the National Institute of Public Health in Cuernavaca, Mexico. Between 2016 and 2017 she pursuit the Specialization in Statistics for Health Sciences, a graduate degree provided by the Calculus Institute in the University of Buenos Aires. In 2017, she earned the Erasmus Summer Program Fellowship and traveled to Rotterdam to spend part of her summer learning from outstanding classes at the National Institute of Health Sciences. This trascendental experience taught her that to address research questions that required complex data, she required further training in advanced epidemiologic methods. For this reason, in 2018 she moved to Rotterdam and started her PhD training at the Epidemiology Department of Erasmus MC under the supervision of Sonja A. Swanson and M. Arfan Ikram, as part of the Causal Inference group and the Neuro-Epidemiology Group. During this time she was immersed in the world of causal inference methods development and had the opportunity to spend time in the Harvard School of Public Health in Boston, USA, as well as in the Leibniz Institute for Prevention Research in Bremen, Germany, collaborating with outstanding and truly kind researchers.

\newpage
